Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper

library(tidyverse)
library(arrow)
library(dplyr)
library(ggplot2)
library(modelsummary)
library(RColorBrewer)
library(future)
library(boot)    # For bootstrapping
library(caret)   # For cross-validation
```

@@

ggplot(harris_data, aes(x = end_date, y = pct, color = factor(numeric_grade))) +
  geom_point(alpha = 0.7) +
  geom_smooth(se = FALSE, span = 0.3) +
  labs(y = "Support for Harris (%)", x = "End Date of the Poll", color = "Numeric Grade") +
  scale_color_viridis_d() +
  theme_classic() +
  theme(legend.position = "bottom") +
  coord_cartesian(ylim = c(0, 100))
```

>>>>

library(tidyverse)
library(arrow)
library(dplyr)
library(ggplot2)
library(modelsummary)
library(RColorBrewer)
library(future)
library(boot)    # For bootstrapping
library(caret)   # For cross-validation
library(knitr)
```

@@

ggplot(harris_data, aes(x = end_date, y = pct, color = factor(numeric_grade))) +
  geom_point(alpha = 0.7) +
  geom_smooth(se = FALSE, span = 0.3) +
  labs(y = "Support for Harris (%)", x = "End Date of the Poll", color = "Numeric Grade") +
  scale_color_viridis_d() +
  theme_classic() +
  theme(legend.position = "bottom") +
  coord_cartesian(ylim = c(0, 100))
```
@tbl-harrissupport shows Harris' average support across states in the 2024 U.S. Presidential Election. She leads in Democratic-leaning states, with top support in Vermont (68.5%), Maryland (62.9%), and Massachusetts (61.2%). In key battlegrounds, Harris's support hovers around 50%, including Wisconsin (49.0%) and Pennsylvania (48.3%). Nationally, she averages 47.9%, with competitive support in swing states like Nevada (47.9%) and North Carolina (47.8%). However, in Republican-leaning states like Texas (44.3%) and Florida (44.2%), her support is lower. This distribution highlights Harris’s strength in Democratic regions and mixed prospects in competitive areas.
```{r}
#| label: tbl-harrissupport
#| tbl-cap: Harris leads in Democratic-leaning states, showing strong support in reliably blue areas. In pivotal swing states, she maintains competitive support, with Wisconsin at 49% and Pennsylvania at 48.3%, reflecting her appeal in regions important for a potential electoral victory. However, in traditionally Republican strongholds, indicating areas where additional campaign efforts might bolster her standing. Nationally, Harris averages 47.9%, underscoring the competitive landscape as election day nears.
#| echo: false
#| warning: false
#| message: false

# Calculate average support for Kamala Harris in each state
harris_data_state <- harris_data|>
  group_by(state)|>
  summarize(`Average Support (%)` = round(mean(pct, na.rm = TRUE), 1)) |>
  arrange(desc(`Average Support (%)`))|>rename(`State` = state)

# Display the result as a table
kable(harris_data_state, caption = "Average Support for Kamala Harris by State")
